A generalized definition of multidimensional item response theory parameters

### 2024-05-28 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects deduction of item direction angles
Corrects deduction of item direction angles in test space
Drops reference to covariance structure
The covariance structure of theta plays no role up to this point, so it must be obviated for now.

Applying Proposition 1, in the test space $`r TEST_SPACE`$, we get

@@

Up to this point,
we have derived the maximum slope and its location in the latent space
$`r LATENT_SPACE`$ independently of its basis $`r LS_BASIS`$.
If we assume $`r BASIS_EQ`$ or, more generally,
that $`r LS_BASIS`$ is orthonormal, $`r TRANSFORM_MATRIX`$ will be
also orthonormal and thus $`r INNER_PROD_MAT_STD_EQ`$.
In such a case the multidimensional item location and discrimination simplify
to the expressions derived by @reckase_difficulty_1985
and @reckase_discriminating_1991.
These expresssions disregard the covariance structure of $`r TRAIT_VECTOR`$ by
implicitly assuming the orthonormality of $`r LS_BASIS`$.
Therefore, we shall refer to these as the *agnostic* version of the indices:

>>>>

Applying Proposition 2, if `r ANGLE_VEC_TS_ITEM` is
the vector of direction angles of `r DISCR_VECTOR`,
in the test space $`r TEST_SPACE`$ we get

@@

Up to this point,
we have derived the maximum slope and its location in the latent space
$`r LATENT_SPACE`$ independently of its basis $`r LS_BASIS`$.
If we assume $`r BASIS_EQ`$ or, more generally,
that $`r LS_BASIS`$ is orthonormal, $`r TRANSFORM_MATRIX`$ will be
also orthonormal and thus $`r INNER_PROD_MAT_STD_EQ`$.
In such a case the multidimensional item location and discrimination simplify
to the expressions derived by @reckase_difficulty_1985
and @reckase_discriminating_1991.
As these expressions implicitly assume the orthonormality of $`r LS_BASIS`$,
which bears no meaning besides its pure algebraic purpose,
we shall refer to them as the *agnostic* version of the indices:
